A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Minor improvement

In this experiment, we needed to match or balance the experimentation
parameters according to the specifications of the algorithm used by the DEAP
library. This is to be able to verify if our algorithm would also converge on
the solutions in a similar number of evaluations and execution time.
Table~\ref{tab1} shows the OneMax initial configuration for DEAP and Life-Cycle
experiment.

>>>>

In our four experiments, we needed to match or balance the experimentation
parameters according to the specifications of the algorithm used by the DEAP
library. This is to be able to verify if our algorithm would also converge on
the solutions in a similar number of evaluations and execution time.
Table~\ref{tab1} shows the OneMax initial configuration for DEAP and Life-Cycle
experiment.
